Procedural generation of levels fot he angry birds videogame using evolutionary computation\\

### 2019-05-14 article_english.tex
Reading proposal

@@

The Since the algorithm has to generate more complex structures the remaining
pieces of a member of the population have to be used has a starting point, this
new additions to the piece pool are added to the population by the mutation
operation, the objective in the first phase of the project is to generate
structures that are capable of maintaining their own balance as shown on figure
3, since the objective of open-ended evolution for this project is to add new
bundles to the pool of options the algorithm will first run a simulation with a
group of pieces and after it the ones that were not destroyed by falling because
of gravity will be saved and added to the pool of options.

@@

>>>>

% Pleas explain in more detail this Composites in a section.

% Please use the name Composite instead of Bundle, composition is well known in
% object oriented design.

@@

% This sentence needs more work -MG
Since the algorithm has to generate more complex structures the remaining
pieces of a member of the population have to be used has a starting point, this
% we don't use member of the populations, use proposed solution, candidate solution
% or individual of the population. - MG  
new additions to the piece pool are added to the population by the mutation
operation, the objective in the first phase of the project is to generate
structures that are capable of maintaining their own balance as shown on figure
3, since the objective of open-ended evolution for this project is to add new
bundles to the pool of options the algorithm will first run a simulation with a
group of pieces and after it the ones that were not destroyed by falling because
of gravity will be saved and added to the pool of options.

% New pieces are added by mutation? 
% Please give more details to all this - MG

@@

% Here it's explained better, maybe this paragraph should be moved to
% an earlier point - MG

% Needs a few touches - MG
